Machine Learning for Predictive Auto-Tuning

### 2011-12-12 paper/draft1.tex
Fix quotes

Due to power consumption and heat dissipation concerns, scientific applications
have shifted from computing platforms where performance had been primarily
driven by rises in the clock frequency of a single “heavy-weight” processor
(with complex out-of-order control and cache structures) to a platform with
ever increasing numbers of “light-weight” cores. Interestingly, this shift is
now not only relevant to computational sciences but to the development of all
computer systems: from ubiquitous consumer-facing devices (e.g. phones) to
high-end computer farms for web-scale applications (e.g. social networks).

>>>>

Due to power consumption and heat dissipation concerns, scientific applications
have shifted from computing platforms where performance had been primarily
driven by rises in the clock frequency of a single ''heavy-weight'' processor
(with complex out-of-order control and cache structures) to a platform with
ever increasing numbers of ''light-weight'' cores. Interestingly, this shift is
now not only relevant to computational sciences but to the development of all
computer systems: from ubiquitous consumer-facing devices (e.g. phones) to
high-end computer farms for web-scale applications (e.g. social networks).
